Abundance/diversity GAM

### 2021-03-15 code/ms1_abundance.Rmd
refined GAM analysis

# 1. Prep work
## 1.1 Prepare environment
```{r setup, include=FALSE, echo=FALSE}
library(mgcv)
library(mgcViz)
library(tidymv)
library(vegan)
library(ggvegan)
library(ggrepel)
library(tidyverse)
library(lubridate)
```

@@

## 1.3 Load network and survey data
```{r message=FALSE}
### BB-FL visitation data
net <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male",
         !bb.sp %in% c("humi", "hypn")) %>% # too rare
  dplyr::select(site, date, bb.sp, plant.sp) # drop unused columns

@@

## 1.5 Calculate binary "preference" for each plant genus by each bumble bee species; score species 0 or 1 based on whether they were visited
```{r message=FALSE}
weights <- fl_abund_sp %>%
  select(plant.sp, plant.genus) %>%
  unique() %>%
  left_join(select(net, bb.sp, plant.sp)) %>%
  select(plant.genus, bb.sp) %>%
  distinct() %>%
  mutate(visited = rep(1, n())) %>%
  pivot_wider(values_from = visited, names_from = bb.sp, values_fill = 0) %>%
  pivot_longer(cols = 2:15, values_to = "visited", names_to = "bb.sp")

@@

ggplot(filter(bb_range2, bb.sp != "humi"), aes(elev.mean, abund)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 6)) +
  facet_wrap(~bb.sp, scales = "free_y", ncol = 4) +
  geom_vline(xintercept = 1500, color = "red", linetype = "dashed")
```

@@

# Join
abund_sum <- full_join(weighted_fl_abund_mean, bb_abund_sp_max) %>%  
  unite(sp.year, c(bb.sp, year), remove = FALSE) %>%
  mutate(site = factor(site),
         bb.sp = factor(bb.sp),
         sp.year = factor(sp.year)) 
```

### 2.2.2 Preliminary visualizations
```{r}
## mean floral abundance
ggplot(abund_sum, aes(elev.mean, mean.fl.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 8), se = FALSE) +
  facet_wrap(~bb.sp, scales = "free_y") +
  geom_vline(xintercept = 1500)

@@

### 2.2.3 Abundance models
#### 2.2.3.1 Bumble bees
```{r}
gam_max_bb_abund_00 <- gam(max.bb.abund ~ 
                             year +
                             s(bb.sp, bs = "re") +
                             s(elev.mean, by = bb.sp, k = 8),
                           method = "REML",
                           family = "nb",
                           select = TRUE,
                           data = abund_sum) %>% getViz()

check.gamViz(gam_max_bb_abund_00)
summary(gam_max_bb_abund_00)
print(plot(gam_max_bb_abund_00, allTerms = TRUE), pages = 1)

gam_max_bb_abund_00_pred <- predict.gam(gam_max_bb_abund_00, type = "terms", se.fit = TRUE) %>%
  as.data.frame() %>%
  as_tibble() %>%
  select(sm.year = 1, sm.bb.sp = 2, gers = 3, hort = 4, jone = 5, lapi = 6, mend  = 7,
         mont = 8, muci = 9, pasc = 10, prat = 11, psit = 12, pyre = 13, soro = 14,
         telu = 15, wurf = 16,
         se.year = 17, se.bb.sp = 18, gers.se = 19, hort.se = 20, jone.se = 21, lapi.se = 22, mend.se  = 23,
         mont.se = 24, muci.se = 25, pasc.se = 26, prat.se = 27, psit.se = 28, pyre.se = 29, soro.se = 30,
         telu.se = 31, wurf.se = 32) %>%
  mutate(fit = sm.year + sm.bb.sp + gers + hort + jone + lapi + 
           mend + mont + muci + pasc + prat + psit + pyre + 
           soro + telu + wurf) %>%
  mutate(se = se.year + se.bb.sp + gers.se + hort.se + jone.se + lapi.se + mend.se + mont.se + 
           muci.se + pasc.se + prat.se + psit.se + pyre.se + soro.se + telu.se + wurf.se) %>%
  select(fit, se) %>%
  mutate(fit.plus = fit + se,
         fit.min = fit - se,
         fit.trans = exp(fit),
         fit.plus.trans = exp(fit.plus),
         fit.min.trans = exp(fit.min)) %>%
  bind_cols(abund_sum)

ggplot(gam_max_bb_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  geom_ribbon(aes(elev.mean, fit.trans, 
                  ymax = fit.plus.trans, ymin = fit.min.trans,
                  fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line() +
  facet_wrap(~bb.sp, scales = "free_y") +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light()
```

#### 2.2.3.2 Floral resources
```{r}
# There are lots of ways this could be specified. From looking at the data and the models, it seems like BB species-level variation in floral resources is very low, and there is a strong global effect of elevation. I think the global model has the strongest message, namely the collapse of overall floral resource availability above the tree line. I can all report the species-level predictions, though.
gam_max_fl_abund_00 <- gam(log(mean.fl.abund) ~ 
                             s(elev.mean, year, bs = "fs", k = 8) +
                             s(elev.mean, bb.sp, bs = "fs", k = 8),
                           method = "REML",
                           family = "gaussian",
                           select = TRUE,
                           data = abund_sum) %>% getViz()

check.gamViz(gam_max_fl_abund_00)
summary(gam_max_fl_abund_00)
concurvity(gam_max_fl_abund_00)
print(plot(gam_max_fl_abund_00, allTerms = TRUE), pages = 1)
plot(gam_max_fl_abund_00)

gam_max_fl_abund_00_pred <- predict.gam(gam_max_fl_abund_00, type = "terms", se.fit = TRUE) %>%
  as.data.frame() %>%
  as_tibble() %>%
  select(sm.year = 1, sm.bb.sp = 2,
         se.year = 3, se.bb.sp = 4) %>%
  mutate(fit = sm.year) %>%
  mutate(se = se.year) %>%
  select(fit, se) %>%
  mutate(fit.plus = fit + se,
         fit.min = fit - se,
         fit.trans = exp(fit),
         fit.plus.trans = exp(fit.plus),
         fit.min.trans = exp(fit.min)) %>%
  bind_cols(na.omit(abund_sum)) %>% # the na.omit() drops the rows where floral surveying data were missing
  select(fit.trans, fit.plus.trans, fit.min.trans, se, elev.mean, year) %>%
  distinct()

ggplot(gam_max_fl_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  geom_ribbon(aes(elev.mean, fit.trans, 
                  ymax = fit.plus.trans, ymin = fit.min.trans,
                  fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line() +
  #geom_point(aes(elev.mean, mean.fl.abund, color = year), inherit.aes = FALSE, alpha = 0.25) +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light()

# Alternatively, since it seems like species basically has just an intercept effect
gam_max_fl_abund_01 <- gam(log(mean.fl.abund) ~ 
                             s(bb.sp, bs = "re") +
                             s(elev.mean, year, bs = "fs", k = 8),
                           method = "REML",
                           family = "gaussian",
                           select = TRUE,
                           data = abund_sum) %>% getViz()

check.gamViz(gam_max_fl_abund_01)
summary(gam_max_fl_abund_01)
concurvity(gam_max_fl_abund_01)
print(plot(gam_max_fl_abund_01, allTerms = TRUE), pages = 1)
plot(gam_max_fl_abund_01)

gam_max_fl_abund_01_pred <- predict.gam(gam_max_fl_abund_00, type = "terms", se.fit = TRUE) %>%
  as.data.frame() %>%
  as_tibble() %>%
  select(sm.year = 1, sm.bb.sp = 2,
         se.year = 3, se.bb.sp = 4) %>%
  mutate(fit = sm.year) %>%
  mutate(se = se.year) %>%
  select(fit, se) %>%
  mutate(fit.plus = fit + se,
         fit.min = fit - se,
         fit.trans = exp(fit),
         fit.plus.trans = exp(fit.plus),
         fit.min.trans = exp(fit.min)) %>%
  bind_cols(na.omit(abund_sum)) %>% # the na.omit() drops the rows where floral surveying data were missing
  select(fit.trans, fit.plus.trans, fit.min.trans, se, elev.mean, year) %>%
  distinct()

ggplot(gam_max_fl_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  geom_ribbon(aes(elev.mean, fit.trans, 
                  ymax = fit.plus.trans, ymin = fit.min.trans,
                  fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line() +
  #geom_point(aes(elev.mean, mean.fl.abund, color = year), inherit.aes = FALSE, alpha = 0.25) +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light()
```

>>>>

# 1. Prep work
## 1.1 Prepare environment
```{r setup, include=FALSE, echo=FALSE}
library(mgcv)
library(mgcViz)
library(tidymv)
library(vegan)
library(ggvegan)
library(ggrepel)
library(ggforce)
library(tidyverse)
library(lubridate)
```

@@

## 1.3 Load network and survey data
```{r message=FALSE}
### BB-FL visitation data
net <- read_csv("../data/processed_data/network.csv") %>%
  filter(caste != "male",
         !bb.sp %in% c("humi", "hypn", "lapi")) %>% # too rare
  dplyr::select(site, date, bb.sp, plant.sp) # drop unused columns

@@

## 1.5 Calculate binary "preference" for each plant genus by each bumble bee species; score species 0 or 1 based on whether they were visited
```{r message=FALSE}
weights <- fl_abund_sp %>%
  select(plant.sp, plant.genus) %>%
  unique() %>%
  left_join(select(net, bb.sp, plant.sp)) %>%
  select(plant.genus, bb.sp) %>%
  distinct() %>%
  mutate(visited = rep(1, n())) %>%
  pivot_wider(values_from = visited, names_from = bb.sp, values_fill = 0) %>%
  pivot_longer(cols = 2:14, values_to = "visited", names_to = "bb.sp")

@@

ggplot(filter(bb_range2, bb.sp != "humi"), aes(elev.mean, abund)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 6)) +
  facet_wrap(~bb.sp, scales = "free_y", ncol = 4) +
  geom_vline(xintercept = 1500, color = "red", linetype = "dashed")

# Overall bumble bee abundance
bb_abund_sum <- bb_abund_sp %>%
  group_by(site, bb.sp) %>%
  summarize(cum.abund = sum(bb.abund),
            mean.abund = mean(bb.abund)) %>%
  group_by(site) %>%
  mutate(prop.abund = cum.abund/sum(cum.abund)) %>%
  group_by(bb.sp) %>%
  mutate(mean.prop.abund = mean(prop.abund))

ggplot(bb_abund_sum, aes(site, prop.abund, fill = bb.sp)) +
  geom_col()

ggplot(bb_abund_sum, aes(bb.sp, mean.abund)) +
  geom_boxplot()

ggplot(bb_abund_sum, aes(reorder(bb.sp, -mean.prop.abund), prop.abund)) +
  geom_boxplot(fill = "gray85") +
  theme_light() +
  ylab("Proportional abundance") +
  xlab("Bumble bee species")

ggsave("../output/bb_abundsum.pdf")
ggsave("../output/bb_abundsum.png")
```

@@

# Join
abund_sum <- full_join(weighted_fl_abund_mean, bb_abund_sp_max) %>%  
  unite(sp.year, c(bb.sp, year), remove = FALSE) %>%
  mutate(site = factor(site),
         bb.sp = factor(bb.sp),
         sp.year = factor(sp.year)) %>%
  unite(bb.sp.year, c(bb.sp, year), sep = "_", remove = FALSE) %>%
  mutate(bb.sp.year = factor(bb.sp.year))
```

### 2.2.2 Preliminary visualizations
```{r}
## mean floral abundance
ggplot(abund_sum, aes(elev.mean, mean.fl.abund, color = year)) +
  geom_point(alpha = 0.5) +
  #geom_smooth(method = "gam", formula = y ~ s(x, k = 8), se = FALSE) +
  facet_wrap(~bb.sp, scales = "free_y") +
  geom_vline(xintercept = 1500)

@@

### 2.2.3 Abundance models
I'm choosing to use site as a random intercept effect in these models because I think that is the correct way to specify a model involving repeated observations (in this case, bumble bee species) within site. The effect of this decision is that the elevation smoother is less influenced by individual sites and converges more strongly toward the mean. This creates less exciting curves, but I think it is a more principled way to model the data and less prone to overfitting. I can have my cake and eat it too, though, by plotting the actual data over the GAM fit so that the strong patterns of certain sites are visible. Then I can talk about the conditional elevation effect and the importance of certain peaks that are likely to be idiosyncrasies of my system (i.e. it would be overfitting to call them elevation effects).

#### 2.2.3.1 Bumble bees
```{r}
# Call model
gam_max_bb_abund_00 <- gam(max.bb.abund ~ 
                             s(bb.sp, bs = "re") +
                             s(bb.sp.year, bs = "re") + # fixed intercept for bb.sp:year
                             s(site, bs = "re") + # random intercept for site
                             s(elev.mean, by = bb.sp, k = 8), # smoother for elev by BB sp.
                           method = "REML",
                           family = "tw", # Tweedie distribution performs well
                           select = TRUE,
                           data = abund_sum) %>% getViz()

gam_max_bb_abund_00_ilink <- family(gam_max_bb_abund_00)$linkinv # get inverse link function

check.gamViz(gam_max_bb_abund_00) # evaluate model
gam_max_bb_abund_00_sum <- summary(gam_max_bb_abund_00) # summarize model
print(plot(gam_max_bb_abund_00, allTerms = TRUE), pages = 1) # preliminary visualization

# Plot smooths and year effect on the link scale
## Individual plots
gers_abund <- plot(sm(gam_max_bb_abund_00, 4)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "gers")
hort_abund <- plot(sm(gam_max_bb_abund_00, 5)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "hort")
jone_abund <- plot(sm(gam_max_bb_abund_00, 6)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "jone")
mend_abund <- plot(sm(gam_max_bb_abund_00, 7)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "mend")
mont_abund <- plot(sm(gam_max_bb_abund_00, 8)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "mont")
muci_abund <- plot(sm(gam_max_bb_abund_00, 9)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "muci")
pasc_abund <- plot(sm(gam_max_bb_abund_00, 10)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "pasc")
prat_abund <- plot(sm(gam_max_bb_abund_00, 11)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "prat")
psit_abund <- plot(sm(gam_max_bb_abund_00, 12)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "psit")
pyre_abund <- plot(sm(gam_max_bb_abund_00, 13)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "pyre")
soro_abund <- plot(sm(gam_max_bb_abund_00, 14)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "soro")
telu_abund <- plot(sm(gam_max_bb_abund_00, 15)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "telu")
wurf_abund <- plot(sm(gam_max_bb_abund_00, 16)) + l_fitLine() + l_ciLine() + 
  labs(x = "Elevation (m.s.l.)", y = "Peak abundance", title = "wurf")

## Arrange on grid plot
grid_bb_abund <- gridPrint(gers_abund, hort_abund, jone_abund, 
                           mend_abund, mont_abund, muci_abund, 
                           pasc_abund, prat_abund, psit_abund, 
                           pyre_abund, soro_abund, telu_abund, 
                           wurf_abund, year_effect)

pdf("../output/gam_max_bb_abund_grid.pdf")
plot(grid_bb_abund)
dev.off()

# Plot model predictions on response scale and add data as points
## Extract and prepare predictions
gam_max_bb_abund_00_pred <- predict.gam(gam_max_bb_abund_00, # get model predictions
                                        type = "terms") %>% 
  as.data.frame() %>% # convert to data frame
  as_tibble() %>% # convert to tibble
  select(sm.bb.sp = 1, sm.bb.sp.year = 2, sm.site = 3, gers = 4, # rename
         hort = 5, jone = 6, mend = 7, mont = 8, 
         muci = 9, pasc = 10, prat = 11, psit = 12, 
         pyre = 13, soro = 14, telu = 15, wurf = 16) %>%
  mutate(fit = # get cumulative fit and se, ignoring site effect 
           sm.bb.sp + sm.bb.sp.year + gers + 
           hort + jone + mend + mont + 
           muci + pasc + prat + psit + 
           pyre + soro + telu + wurf 
           ) %>%
  select(fit) %>%
  mutate(fit.trans = gam_max_bb_abund_00_ilink(fit)) %>%
  bind_cols(abund_sum)

## Plot
ggplot(gam_max_bb_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  # geom_ribbon(aes(elev.mean, fit.trans, 
  #                 ymax = fit.plus.trans, ymin = fit.min.trans,
  #                 fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line(size = 1.5, alpha = 0.5) +
  geom_point(aes(elev.mean, max.bb.abund, color = year), inherit.aes = FALSE, alpha = 0.25) +
  facet_wrap(~bb.sp, scales = "free_y") +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light() +
  labs(x = "Elevation (m.s.l.)", 
       y = bquote("Peak abundance"),
       color = "Year",
       fill = "Year")

ggsave("../output/gam_max_bb_abund.pdf", width = 6.5, height = 4.5)
ggsave("../output/gam_max_bb_abund.png", width = 6.5, height = 4.5)
```

#### 2.2.3.2 Floral resources
```{r}
gam_mean_fl_abund_00 <- gam(mean.fl.abund ~ 
                             s(site, bs = "re") + # random intercept for site
                             s(elev.mean, year, bs = "fs", k = 8) +
                             s(elev.mean, bb.sp, bs = "fs", k = 8),
                           method = "REML",
                           family = "tw",
                           select = TRUE,
                           data = abund_sum) %>% getViz()

gam_mean_fl_abund_00_ilink <- family(gam_mean_fl_abund_00)$linkinv # get inverse link function

check.gamViz(gam_mean_fl_abund_00) # evaluate model
gam_mean_fl_abund_00_sum <- summary(gam_mean_fl_abund_00) # summarize model
print(plot(gam_mean_fl_abund_00, allTerms = TRUE), pages = 1) # preliminary visualization

# Plot on the link scale
elev_effect <- plot(sm(gam_mean_fl_abund_00, 2)) + l_fitLine(alpha = 0.6, size = 1)
bb.sp_effect <- plot(sm(gam_mean_fl_abund_00, 3)) + l_fitLine(alpha = 0.6, size = 1)

grid_fl_abund <- gridPrint(elev_effect, bb.sp_effect)

pdf("../output/gam_mean_fl_abund_grid.pdf")
plot(grid_fl_abund)
dev.off()

# Plot model predictions on response scale and add data as points
## Extract and prepare predictions
gam_mean_fl_abund_00_pred <- predict.gam(gam_mean_fl_abund_00, 
                                         type = "terms", 
                                         se.fit = TRUE) %>% # get model predictions and se
  as.data.frame() %>% # convert to data frame
  as_tibble() %>% # convert to tibble
  select(sm.site = 1, sm.year = 2, sm.bb.sp = 3, # rename
         se.site = 4, se.year = 5, se.bb.sp = 6) %>%
  mutate(fit = sm.year, # get fit and se ignoring site and species
         se = se.year) %>% 
  select(fit, se) %>%
  mutate(fit.plus = fit + se, # upper CI bound
         fit.min = fit - se, # lower CI bound
         fit.trans = gam_mean_fl_abund_00_ilink(fit), # apply inverse link function
         fit.plus.trans = gam_mean_fl_abund_00_ilink(fit.plus),
         fit.min.trans = gam_mean_fl_abund_00_ilink(fit.min)) %>%
  bind_cols(na.omit(abund_sum)) %>% # the na.omit() drops the rows where floral surveying data were missing
  select(fit.trans, fit.plus.trans, fit.min.trans, 
         se, elev.mean, year, mean.fl.abund) %>%
  distinct()

ggplot(gam_mean_fl_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  # geom_ribbon(aes(elev.mean, fit.trans, 
  #                 ymax = fit.plus.trans, ymin = fit.min.trans,
  #                 fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line(size = 1.5, alpha = 0.5) +
  geom_point(aes(elev.mean, mean.fl.abund, color = year), inherit.aes = FALSE, alpha = 0.15) +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light() +
  labs(x = "Elevation (m.s.l.)", 
       y = bquote("Mean flower cover" ~ (m^2)),
       color = "Year",
       fill = "Year")

ggsave("../output/gam_mean_fl_abund.pdf")
ggsave("../output/gam_mean_fl_abund.png")

ggplot(gam_mean_fl_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  # geom_ribbon(aes(elev.mean, fit.trans, 
  #                 ymax = fit.plus.trans, ymin = fit.min.trans,
  #                 fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line(size = 1.5, alpha = 0.5) +
  geom_point(aes(elev.mean, mean.fl.abund, color = year), inherit.aes = FALSE, alpha = 0.15) +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light() +
  labs(x = "Elevation (m.s.l.)", 
       y = bquote("Mean flower cover" ~ (m^2)),
       color = "Year",
       fill = "Year") +
  ylim(c(0, 10))

ggsave("../output/gam_mean_fl_abund_sub.pdf")
ggsave("../output/gam_mean_fl_abund_sub.png")

ggplot(gam_mean_fl_abund_00_pred, aes(elev.mean, fit.trans, color = year)) +
  # geom_ribbon(aes(elev.mean, fit.trans, 
  #                 ymax = fit.plus.trans, ymin = fit.min.trans,
  #                 fill = year), alpha = 0.2, inherit.aes = FALSE) +
  geom_line(size = 1.5, alpha = 0.5) +
  geom_point(aes(elev.mean, mean.fl.abund, color = year), inherit.aes = FALSE, alpha = 0.15) +
  geom_vline(xintercept = 1500, linetype = "dashed") +
  theme_light() +
  labs(x = "Elevation (m.s.l.)", 
       y = bquote("Mean flower cover" ~ (m^2)),
       color = "Year",
       fill = "Year") +
  facet_zoom(ylim = c(0, 10), 
             show.area = FALSE,
             zoom.size = 1)

ggsave("../output/gam_mean_fl_abund_zoom.pdf", width = 6.5, height = 4.5)
ggsave("../output/gam_mean_fl_abund_zoom.png", width = 6.5, height = 4.5)
```
